Paper Codes

### 2024-04-08 paper_codes.Rmd
plots

```{r}
colors = c("#1f77b4","#64a9d9","#bfe4ff",
          "#ff7f0e","#ffae66","#ffddbf",
          "#2ca02c","#6acf6a","#bfffbf",
          "#d62627","#ea6d6e","#ffbfbf",
          "#9466bd","#b88fde","#e0bfff")
names(colors) = c('Closed estuaries',
 'Dunes mainland',
 'Dunes Wadden islands',
 'Higher sandy soils East',
 'Higher sandy soils North',
 'Higher sandy soils South',
 'Higher sandy soils Veluwe',
 'Hill country Limburg ',
 'Low peat Holland',
 'Low peat North',
 'River area ',
 'Sea clay middle',
 'Sea clay North',
 'Sea clay South ',
 'Tidal areas Zeeland')
ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1, fill=lmf_english,linewidth=0.1,colour=""), data=sf.grid) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Physical Geological Region') +
  scale_colour_manual(values=NA) +
  guides(colour=guide_legend("Not mappable", override.aes=list(colour="gray"))) +
  scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") #+ggtitle('Grid of Netherlands: Landuse') 
ggsave('results_paper/fgr.png', width=1600, heigh=1500, units='px')
```

```{r}
prov_geom <- read_sf("provincies.gpkg")$geom
prov_geom <- (prov_geom - matrix(data=c(155000, 463000), ncol=2)) * matrix(data=c(1/1000, 1/1000), ncol=2)
colors = c("#1f77b4","#aec7e8",
          "#ff7f0e","#ffba78",
          "#2ca02c","#98df8a",
          "#d62627","#ff9896",
          "#9466bd","#c5b0d5",
          "#8c564b","#c49c94")
names(colors) = c('Drenthe',
 'Flevoland',
 'Fryslân',
 'Gelderland',
 'Groningen',
 'Limburg',
 'Noord-Brabant',
 'Noord-Holland',
 'Overijssel',
 'Utrecht',
 'Zeeland',
 'Zuid-Holland')
ggplot() + 
	geom_sf(aes(geometry=geometry.1, fill=naam,linewidth=0.1), data=sf.grid) +
  geom_sf(aes(geometry=prov_geom),fill=NA) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Province') +
  scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") #+ggtitle('Grid of Netherlands: Landuse') 
ggsave('results_paper/provinces.png', width=1600, heigh=1200, units='px')

@@

```{r}
ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1), data=sf.grid) + 
	#geom_sf(aes(geometry=geometry), shape=3, size=0.3, data=sf.grid) + 
	geom_sf(aes(geometry=geometry, color=has_abiotics), shape=4, size=0.5, data=sf.plots) + 
	theme(plot.title = element_text(hjust = 0.5), legend.title=element_text(size=10), 
		legend.text=element_text(size=8), legend.position="right") +
	scale_colour_manual(values=c("#377EB8", "#4DAF4A"), name="Has abiotics") #+ 
	#ggtitle('Location of Field Visits and Abiotics') 
ggsave('results_paper/visits.png', width=1400, heigh=1200, units='px')

@@

```{r}
colors = c("#1f77b4","#64a9d9","#bfe4ff",
          "#ff7f0e","#ffae66","#ffddbf",
          "#2ca02c","#6acf6a","#bfffbf",
          "#d62627","#ea6d6e","#ffbfbf",
          "#9466bd","#b88fde","#e0bfff")
names(colors) = c('Closed estuaries',
 'Dunes mainland',
 'Dunes Wadden islands',
 'Higher sandy soils East',
 'Higher sandy soils North',
 'Higher sandy soils South',
 'Higher sandy soils Veluwe',
 'Hill country Limburg ',
 'Low peat Holland',
 'Low peat North',
 'River area ',
 'Sea clay middle',
 'Sea clay North',
 'Sea clay South ',
 'Tidal areas Zeeland')
plot.validation.2 <- ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1, fill=lmf_english,linewidth=0.1,colour=""), data=sf.grid) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Physical Geological Region') +
  scale_colour_manual(values=NA) +
  guides(colour=guide_legend("Not mappable", override.aes=list(colour="gray"))) +
  scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") +ggtitle('Leave-FGR-out')

prov_geom <- read_sf("provincies.gpkg")$geom
prov_geom <- (prov_geom - matrix(data=c(155000, 463000), ncol=2)) * matrix(data=c(1/1000, 1/1000), ncol=2)
colors = c("#1f77b4","#aec7e8",
          "#ff7f0e","#ffba78",
          "#2ca02c","#98df8a",
          "#d62627","#ff9896",
          "#9466bd","#c5b0d5",
          "#8c564b","#c49c94")
names(colors) = c('Drenthe',
 'Flevoland',
 'Fryslân',
 'Gelderland',
 'Groningen',
 'Limburg',
 'Noord-Brabant',
 'Noord-Holland',
 'Overijssel',
 'Utrecht',
 'Zeeland',
 'Zuid-Holland')
plot.validation.1 <- ggplot() + 
	geom_sf(aes(geometry=geometry.1, fill=naam,linewidth=0.1), data=sf.grid) +
  geom_sf(aes(geometry=prov_geom),fill=NA) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Province') +
  scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") +ggtitle('Leave-province-out')

# Combine plots
plot.all <- ggdraw() +
  draw_plot(plot.validation.1, x = 0, y = 0, width = 0.50, height = 1) +
  draw_plot(plot.validation.2, x = 0.49, y = 0, width = 0.55, height = 1) +
  draw_plot_label(label = c("A", "B"), size = 15, x = c(0.01, 0.50), y = c(0.99,0.99)) +
  theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all
ggsave('results_paper/leave_out_validation.png', width=4600, heigh=1800, units='px')

>>>>

```{r}
colors = c("#1f77b4","#64a9d9","#bfe4ff",
          "#ff7f0e","#ffae66","#ffddbf",
          "#2ca02c","#6acf6a","#bfffbf",
          "#d62627","#ea6d6e","#ffbfbf",
          "#9466bd","#b88fde","#e0bfff")
names(colors) = c('Closed estuaries',
 'Dunes mainland',
 'Dunes Wadden islands',
 'Higher sandy soils East',
 'Higher sandy soils North',
 'Higher sandy soils South',
 'Higher sandy soils Veluwe',
 'Hill country Limburg ',
 'Low peat Holland',
 'Low peat North',
 'River area ',
 'Sea clay middle',
 'Sea clay North',
 'Sea clay South ',
 'Tidal areas Zeeland')
ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1, fill=lmf_english,linewidth=0.1,colour=""), data=sf.grid) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Physical Geological Region') +
  scale_colour_manual(values=NA) +
  guides(colour=guide_legend("Not mappable", override.aes=list(colour="gray"))) +
  scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") +ggtitle('Physical Geographical Regions') 
ggsave('results_paper/fgr.png', width=1600, heigh=1500, units='px')
```

```{r}
prov_geom <- read_sf("provincies.gpkg")$geom
prov_geom <- (prov_geom - matrix(data=c(155000, 463000), ncol=2)) * matrix(data=c(1/1000, 1/1000), ncol=2)
colors = c("#1f77b4","#aec7e8",
          "#ff7f0e","#ffba78",
          "#2ca02c","#98df8a",
          "#d62627","#ff9896",
          "#9466bd","#c5b0d5",
          "#8c564b","#c49c94")
names(colors) = c('Drenthe',
 'Flevoland',
 'Fryslân',
 'Gelderland',
 'Groningen',
 'Limburg',
 'Noord-Brabant',
 'Noord-Holland',
 'Overijssel',
 'Utrecht',
 'Zeeland',
 'Zuid-Holland')
ggplot() + 
	geom_sf(aes(geometry=geometry.1, fill=naam,linewidth=0.1), data=sf.grid) +
  geom_sf(aes(geometry=prov_geom),fill=NA) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Province') +
  scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") +ggtitle('Provinces of the Netherlands')  
ggsave('results_paper/provinces.png', width=1600, heigh=1200, units='px')

@@

```{r}
sf.plots.rev <- sf.plots %>% arrange(has_abiotics)
ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1), data=sf.grid) + 
	#geom_sf(aes(geometry=geometry), shape=3, size=0.3, data=sf.grid) + 
	geom_sf(aes(geometry=geometry, color=has_abiotics), shape=4, size=0.5, data=sf.plots.rev) + 
	theme(plot.title = element_text(hjust = 0.5), legend.title=element_text(size=10), 
		legend.text=element_text(size=8), legend.position="right") +
	scale_colour_manual(values=c("#377EB8", "#4DAF4A"), name="Abiotic measurements") +
  scale_fill_discrete(guide=guide_legend(reverse=T))
	#ggtitle('Location of Field Visits and Abiotics') 
ggsave('results_paper/visits.png', width=1400, heigh=1200, units='px')

@@

```{r}
colors = c("#1f77b4","#64a9d9",
          "#ff7f0e","#ff9e49","#ffbd84","#ffddbf",
          "#2ca02c",
          "#d62627","#ea6d6e",
          "#8c564b",
          "#9466bd","#b88fde","#e0bfff")
names(colors) = c(
 'Dunes mainland', 'Dunes Wadden islands',
 'Higher sandy soils East', 'Higher sandy soils North', 'Higher sandy soils South', 'Higher sandy soils Veluwe',
 'Hill country Limburg ',
 'Low peat Holland', 'Low peat North',
 'River area ',
 'Sea clay middle', 'Sea clay North', 'Sea clay South ')
plot.validation.2 <- ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1, fill=lmf_english,linewidth=0.1,colour=""), data=filter(sf.grid, lmf_english!='Tidal areas Zeeland', lmf_english!='Closed estuaries')) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Physical Geological Region') +
  scale_colour_manual(values=NA) +
  guides(colour=guide_legend("Not mappable", override.aes=list(colour="gray"))) +
  # scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  # scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") +ggtitle('Leave-FGR-out')

prov_geom <- read_sf("provincies.gpkg")$geom
prov_geom <- (prov_geom - matrix(data=c(155000, 463000), ncol=2)) * matrix(data=c(1/1000, 1/1000), ncol=2)
colors = c("#1f77b4","#aec7e8",
          "#ff7f0e","#ffba78",
          "#2ca02c","#98df8a",
          "#d62627","#ff9896",
          "#9466bd","#c5b0d5",
          "#8c564b","#c49c94")
names(colors) = c('Drenthe',
 'Flevoland',
 'Fryslân',
 'Gelderland',
 'Groningen',
 'Limburg',
 'Noord-Brabant',
 'Noord-Holland',
 'Overijssel',
 'Utrecht',
 'Zeeland',
 'Zuid-Holland')
plot.validation.1 <- ggplot() + 
	geom_sf(aes(geometry=geometry.1, fill=naam,linewidth=0.1), data=sf.grid) +
  geom_sf(aes(geometry=prov_geom),fill=NA) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Province') +
  # scale_y_continuous(breaks = c(-100,0, 100), labels = c("363000","463000", "563000")) +
  # scale_x_continuous(breaks = c(-100,0, 100), labels = c("55000","155000", "255000")) +
	theme(legend.position="right") +ggtitle('Leave-province-out')

# Combine plots
plot.all <- ggdraw() +
  draw_plot(plot.validation.1, x = 0.01, y = 0, width = 0.47, height = 1) +
  draw_plot(plot.validation.2, x = 0.47, y = 0, width = 0.53, height = 1) +
  draw_plot_label(label = c("A", "B"), size = 15, x = c(0.0, 0.455), y = c(0.99,0.99)) +
  theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all
ggsave('results_paper/leave_out_validation.png', width=3400, heigh=1400, units='px')
